Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-01 yfcc100m/paper/vldb2020/eval.tex
Update eval and comparison system figure

@@

>>>>

For all our experiments, we use 2 servers, one hosting VDMS server and
another hosting MySQL server. Both servers have a dual-socket INTEL XEON XXXXX,
each cpu with 28 physical cores with multithreading enabeled,
for a total of 112 logical cores per server.
The server hosting MySQL has 256GB of DDR4 DRAM, while the server hosting VDMS
has 64GB of DDR4 DRAM. Both servers run Ubuntu 16.04.
We use MySQL version XXXXX.

Figure \ref{figure:systems} shows a logical view of the difference between the
interaction of the client application (which wants to retrieve metadata and
imaged) with VDMS (left) and MySQL + Apache HTTP Server (right).
It is worth noting that the images are stored in a shared repository
(ext4 filesystem on a RAID 6 configuration of 16TB) that both Apache WebServer
and VDMS have direct access. In the case of MySQL, metadata is stored in an
attached SSD disk. Even if VDMS has native support for Optane Persistent Memory,
we do not use it in this experiment because of fairness of comparison w.r.t
MySQL. The benefits of Persistent Memory on metadata operations is left
for another paper, and outside the scope of this evaluation.
For this experiment then, we simply use a similar attached SSD disk to store
metadata (even if VDMS Graph store is designed for PM, it can deliver good
performance when using SSDs directly).

@@

% \begin{tabular}{c c c c c}
% \hline\hline
%  & \multicolumn{2}{c}{Building Metadata Time} & \multicolumn{2}{c}{Metadata Size}\\
% \cline{2-3} \cline{4-5}%\hline
% Database Size & MySQL & VDMD & MySQL & VDMS\\
% \hline
% 100k & 0.2   & 0.1  & 0.173 & 0.226\\
% 500k & 1.1   & 0.4  & 0.805 & 1.1\\
% 1M   & 2.2   & 0.6  & 1.6   & 2.2\\
% 5M   & 11.7  & 3.0  & 7.8   & 11\\
% 10M  & 22.1  & 6.0  & 16    & 22\\
% 50M  & 147.1 & 24.2 & 78    & 109\\
% 100M & 263.0 & 72.5 & 163   & 228\\
% \hline
% \end{tabular}
% \label{table:metadata}
% \end{table*}

### 2020-02-01 yfcc100m/paper/vldb2020/vdms-vldb2020.tex
Add more figures and other minor additions
Added build time table, vdms/mysql edge/row tables, and initial build notes
Update eval and comparison system figure

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% Authors
\alignauthor
Luis Remis\titlenote{Most of the work was done while at Intel Labs.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{ApertureData Inc.}\\
       \email{luis@aperturedata.io}
\alignauthor
Chaunte Lacewell\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
       \affaddr{Intel Labs}\\
       \email{chaunte.w.lacewell@intel.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
%(The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{abstract}
We introduce the Visual Data Management System (VDMS),
which enables faster access to big-{\em visual}-data
and adds support to visual analytics.
This is achieved by searching for relevant visual data via metadata stored as
a graph, and enabling faster access to visual data through new
machine-friendly storage formats. VDMS differs from existing large scale photo
serving, video streaming, and textual big-data management systems due to
its primary focus on supporting machine learning and
data analytics pipelines that use visual data
(images, videos, and feature vectors), treating these as first class entities.
We describe how to use VDMS via its user friendly interface and how
it enables rich and efficient vision analytics through a machine learning
pipeline for processing medical images. We show the improved
performance of 2x in complex queries over a comparable set-up.
\end{abstract}

\input{intro.tex}
\input{design.tex}
%\input{demo.tex}
%\input{conclusion.tex}

@@

>>>>

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% Authors
\alignauthor
Luis Remis\titlenote{Most of the work was done while at Intel Labs.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{ApertureData Inc.}\\
       \email{luis@aperturedata.io}
\alignauthor
Chaunt\'e W. Lacewell\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
       \affaddr{Intel Labs}\\
       \email{chaunte.w.lacewell@intel.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group, {\texttt{jsmith@affiliation.org}}), Julius P.~Kumquat
%(The \raggedright{Kumquat} Consortium, {\small \texttt{jpkumquat@consortium.net}}), and Ahmet Sacan (Drexel University, {\small \texttt{ahmetdevel@gmail.com}})}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{abstract}
Data scientists spend most of their time dealing with data preparation,
rather than doing what they know best:
build machine learning models and algorithms to solve problems.
The problem grows as the scale of the data that is used for analysis or training
grows. In this paper, we demonstrate how VDMS (Visual Data Management System)
can be used to simplify the data preparation process and we show how we gain
in efficient just because we are using a tool that was design for the job.
To demonstrate this, we use the largest available public dataset (YFCC100M),
with 99+ million images, 800+ thousand videos plus add-ons that include
machine-generated tags and 4K dimensional feature vectors,
a total of ± 13TB of data.
VDMS differs from existing large scale photo
serving, video streaming, and textual big-data management systems due to
its primary focus on supporting machine learning and
data analytics pipelines that use visual data
(images, videos, and feature vectors), treating these as first class citizens.
We demonstrate how VDMS outperforms well-know and widely used tools for
data access by a 10x factor in certain queries, while simplifying the process
of data preparation and data access, and providing functionalities non-existent
in alternative options.
\end{abstract}

\input{intro.tex}
\input{design.tex}
\input{eval.tex}
%\input{demo.tex}
\input{conclusion.tex}

@@

\clearpage
